Run-Time Monitoring with Adjustable Overheads Using Dataflow-Guided Filtering

### 2014-09-12 dropping.tex
Double-check for consistent figure fonts.
Various edits based on Ed's comments.

Figure~\ref{fig:dropping.overview} shows an overview of the run-time monitoring
model that is assumed in this paper.  The \emph{main program} is a computation
task that performs the original function of the system and is run on the
\emph{main core}.  On certain events during the main program, such as the
execution of certain types of instructions, the \emph{monitor} performs a
series of \emph{monitoring operations}. The monitor operates in parallel to the
main core. These events are referred to as \emph{monitoring events}. Depending
on the type of monitoring event, different monitoring operations are
executed. Information about monitoring events is sent to the monitor and buffered in a FIFO structure to decouple the
running of the main core and the monitor. If the FIFO is full, then the main
core is forced to stall on a monitoring event until a FIFO entry becomes
available. These stalls are a major source of
overhead because the monitor may take several cycles to process a single event
from the main core. 
Monitors typically maintain a set of metadata corresponding to the main
program's memory. Similarly, monitors also typically maintain a set of metadata
corresponding to the main core's register file.
%We refer to these stalls and other overheads, such as
%contention for shared resources, as \emph{monitoring overheads}. 
If the monitor
detects an inconsistent or undesired behavior in the monitoring events, then
an error is detected.

@@

Figure~\ref{fig:dropping.example_full} shows an example pseudo-code segment,
its assembly level instructions, and the corresponding monitoring operations
for an array bounds check monitor. 
First, an array {\tt x} is allocated using {\tt malloc}. 
As {\tt malloc} returns the array's address in a register, the monitor
associates base and bounds metadata with the corresponding metadata. 
Next, pointer {\tt y} is set to point to the middle of array {\tt x}. 
At the assembly level, a register {\tt r2} is set to array {\tt x}'s address plus an offset.
The monitor propagates the metadata of the original pointer in {\tt r1} to the
metadata of {\tt r2}. This is to ensure that pointer {\tt y} is not used to exceed the array's bounds.
Finally, both pointers {\tt x} and {\tt y} are used to perform a write. 
This requires setting register {\tt r3} to the write value. When this happens,
{\tt r3}'s metadata is also reset to NULL in case it previously stored a
pointer. In both cases, the monitor checks whether the address that is written
to is within the bounds stored in the metadata. In the first case, {\tt x+12}
is within the original array's bounds. No error is raised and the metadata of
{\tt r3} is propagated to the metadata of the store address. If {\tt r3} were a
pointer, than this would allow a future instruction to load the pointer and use
it to access the corresponding array or data structure. In the second case,
{\tt y+12} corresponds to {\tt x+20} which is not within the array's bounds and
the monitor will raise an error.

@@

The key cause of false positives is dropping monitoring operations that update
metadata. Dropping monitoring operations that check for an error (such as check
found for line 4 in Figure~\ref{fig:dropping.example_full} can only cause
false negatives but will never cause false positives. On the other hand,
skipping monitoring operations that update metadata can lead to false positives
and false negatives.
Essentially, when an update operation is skipped, we can no longer trust the
corresponding metadata. Thus, our general approach for preventing false positives is to mark these metadata as
invalid. Furthermore, this invalidation information is propagated in the same
way that metadata is. Figure~\ref{fig:dropping.example_invalid}
shows an example of associating invalid flags with metadata. In the example, no
monitoring operations are dropped. However, suppose that the monitoring for
line 1 is dropped. In this case, {\tt rf\_invalid[1]} will be marked as {\tt
true}. Thus, when line 3 is reached, the monitoring event is dropped
since {\tt rf\_invalid[1]} is marked as true. Note that in this case, line 2
also propagates this invalid flag to {\tt rf\_invalid[2]} and causes the check
performed on line 4 to also be dropped. This is necessary because an error
would have been raised even if the access on line 4 was in bounds.

@@

% Detailed architecture of dataflow engine
\begin{figure*}
  \begin{center}
    \includegraphics[width=\linewidth]{figs/dataflow_architecture.pdf}
    \vspace{-0.2in}
    \caption{Hardware architecture of the dataflow engine.}
    \label{fig:dropping.dataflow} 
    \vspace{-0.1in}
  \end{center}
\end{figure*}

Thus, the hardware acts effectively as a dataflow tracking engine in order to
track invalid flags. Figure~\ref{fig:dropping.dataflow} shows a detailed block
diagram of this hardware module. The dataflow engine uses two address
calculation units to read in up two invalid flags. These source invalid flags
are used to decide whether a monitoring event should filtered. A third address
calculation unit is used to optionally specify a target to propagate the
invalidation information. The module includes a register file to store invalid
flags corresponding to register file metadata. In addition, it uses a small
memory-backed cache to handle invalid flags corresponding to memory metadata.

@@

One way to reduce the number of monitoring events that must be handled by the
monitor is to filter out monitoring events that correspond to operating on null
or uninitialized metadata. Null metadata typically corresponds to events that
are not relevant to the monitor. For example, Hardbound
\cite{hardbound-asplos08} filters out operations on non-pointer (i.e., no base
and bounds metadata) instructions since it is not relevant to array bounds
checking. More recently, FADE \cite{fade-hpca14} has been proposed a general
hardware module to perform this null metadata filtering for a variety of
monitoring schemes.

@@

The operations performed by null filtering are almost identical to the
operations needed for invalidation shown in
Figure~\ref{fig:dropping.example_invalid}.
Thus, we can easily enable this null metadata filtering on our architecture by
simply extending the dataflow flags to be two bits wide. One bit is used to
keep track of invalidation information while the second bit is used to keep
track of null information. All flags are initialized to null and the filter
decision table is extended with the propagation and filtering decision rules
for null metadata filtering.

>>>>

Figure~\ref{fig:dropping.overview} shows an overview of the run-time monitoring
model that is assumed in this paper.  The \emph{main program} is a computation
task that performs the original function of the system and is run on the
\emph{main core}.  On certain events during the main program, such as the
execution of certain types of instructions, the \emph{monitor} performs a
series of \emph{monitoring operations}. The monitor operates in parallel to the
main core. These events are referred to as \emph{monitoring events}. Depending
on the type of monitoring event, different monitoring operations are
executed. Information about monitoring events is sent to the monitor and buffered in a FIFO structure to decouple the
running of the main core and the monitor. If the FIFO is full, then the main
core is forced to stall on a monitoring event until a FIFO entry becomes
available. These stalls are a major source of
overhead because the monitor may take several cycles to process a single event
from the main core. 
Monitors typically maintain a set of metadata corresponding to the main
program's memory. Similarly, monitors also typically maintain a set of metadata
corresponding to the main core's register file.
%We refer to these stalls and other overheads, such as
%contention for shared resources, as \emph{monitoring overheads}. 
Monitors typically maintain metadata corresponding to each memory location
({\tt mem\_metadata[addr]}) and register ({\tt rf\_metadata[reg\_id]}) of the
main core.
If the monitor
detects an inconsistent or undesired behavior in the monitoring events, then
an error is detected.

@@

Figure~\ref{fig:dropping.example_full} shows an example pseudo-code segment,
its assembly level instructions, and the corresponding monitoring operations
for an array bounds check monitor. 
First, an array {\tt x} is allocated using {\tt malloc} (line 1). 
As {\tt malloc} returns the array's address in a register, the monitor
associates base and bounds metadata with the corresponding metadata. 
Next, pointer {\tt y} is set to point to the middle of array {\tt x} (line 2). 
At the assembly level, a register {\tt r2} is set to array {\tt x}'s address plus an offset.
The monitor propagates the metadata of the original pointer in {\tt r1} to the
metadata of {\tt r2}. This is to ensure that pointer {\tt y} is not used to exceed the array's bounds.
Line 3a shows setting register {\tt r3} to a constant value of 1.
When this happens,
{\tt r3}'s metadata is also reset to NULL in case it previously stored a
pointer. 
Finally, the value of {\tt r3} is written using both pointers {\tt x} and {\tt y}.
In both cases, the monitor checks whether the address that is written
to is within the bounds stored in the metadata. In the first case (line 3b), {\tt x+12}
is within the original array's bounds. No error is raised and the metadata of
{\tt r3} is propagated to the metadata of the store address. If {\tt r3} were a
pointer, than this would allow a future instruction to load the pointer and use
it to access the corresponding array or data structure. In the second case,
{\tt y+12} (line 4) corresponds to {\tt x+20} which is not within the array's bounds and
the monitor will raise an error.

@@

The key cause of false positives is dropping monitoring operations that update
metadata. Dropping monitoring operations that check for an error (such as check
found for line 4 in Figure~\ref{fig:dropping.example_full} can only cause
false negatives but will never cause false positives. On the other hand,
skipping monitoring operations that update metadata can lead to false positives
and false negatives.
Essentially, when an update operation is skipped, we can no longer trust the
corresponding metadata. Thus, our general approach for preventing false
positives is to add a 1-bit flag to each metadata in order to mark these
metadata as
invalid. Furthermore, this invalidation information is propagated in the same
way that metadata is. Figure~\ref{fig:dropping.example_invalid}
shows an example of associating invalid flags with metadata. In the example, no
monitoring operations are dropped. However, suppose that the monitoring for
line 1 is dropped. In this case, {\tt rf\_invalid[1]} will be marked as {\tt
true}. Thus, when line 3 is reached, the monitoring event is dropped
since {\tt rf\_invalid[1]} is marked as true. Note that in this case, line 2
also propagates this invalid flag to {\tt rf\_invalid[2]} and causes the check
performed on line 4 to also be dropped. This is necessary because an error
would have been raised even if the access on line 4 was in bounds.

@@

% Detailed architecture of dataflow engine
\begin{figure*}
  \begin{center}
    \includegraphics[]{figs/dataflow_architecture.pdf}
    \vspace{-0.2in}
    \caption{Hardware architecture of the dataflow engine.}
    \label{fig:dropping.dataflow} 
    \vspace{-0.1in}
  \end{center}
\end{figure*}

Thus, the hardware acts effectively as a dataflow tracking engine in order to
track a 1-bit invalid flag per metadata. Figure~\ref{fig:dropping.dataflow} shows a detailed block
diagram of this hardware module. The dataflow engine uses two address
calculation units to read in up two invalid flags. These source invalid flags
are used to decide whether a monitoring event should filtered. A third address
calculation unit is used to optionally specify a target to propagate the
invalidation information. The module includes a register file to store invalid
flags corresponding to register file metadata. In addition, it uses a small
memory-backed cache to handle invalid flags corresponding to memory metadata.

@@

One way to reduce the number of monitoring events that must be handled by the
monitor is to filter out monitoring events that correspond to operating on null
metadata. Null metadata corresponds to events that
are not relevant to the monitor. For example, Hardbound
\cite{hardbound-asplos08} filters out operations on non-pointer (i.e., no base
and bounds metadata) instructions since it is not relevant to array bounds
checking. More recently, FADE \cite{fade-hpca14} has been proposed a general
hardware module to perform this null metadata filtering for a variety of
monitoring schemes.

@@

The operations performed by null filtering are almost identical to the
operations needed for invalidation shown in
Figure~\ref{fig:dropping.example_invalid}. Instead of taking a logical OR of the
source invalid flags to determine whether monitoring can be skipped, null
metadata filtering takes a logical AND of the source null flags.
Thus, we can easily enable this null metadata filtering on our architecture by
extending the dataflow flags to be two bits wide. One bit is used to
keep track of invalidation information while the second bit is used to keep
track of null information. All flags are initialized to null and the filter
decision table is extended with the propagation and filtering decision rules
for null metadata filtering.
The results is a single hardware design that provides enables both partial
monitoring and null metadata filtering.

### 2014-09-12 evaluation.tex
Various edits based on Ed's comments.

We implemented our dataflow-guided monitoring architecture by
modifying the ARM version of the gem5 simulator \cite{gem5} to support parallel
run-time monitoring. We model the main and monitoring cores as running at 2.5
GHz with 4-way set-associative private L1 I/D caches and a shared 8-way 2 MB L2
cache. This setup is similar to the Snapdragon 801 processor commonly found in
mobile systems. The dataflow engine uses a 1 kB cache for flags.

In order to explore the generality of the architecture for
different monitors, we implemented four different monitors: uninitialized
memory check (UMC), array bounds check (BC), dynamic information flow
tracking (DIFT), instruction-mix profiling (IMP), and LockSet-based race detection (LS).  Uninitialized memory
check seeks to detect loading from
memory locations that are not initialized first. Array bounds check, as
mentioned in Section~\ref{sec:monitoring}, is a monitoring scheme that aims to
detect buffer overflows where memory accesses go beyond the boundaries of an
array. We modify the implementation of {\tt malloc} to set base and bound
metadata information. Dynamic information flow tracking is a security
monitoring scheme
which detects when information from untrusted sources is used to affect the
program control flow (i.e., indirect control instructions). For the benchmarks we consider, we mark data read from
files as untrusted. We implemented a multi-bit DIFT scheme which marks
untrusted data with a 32-bit metadata identifier so
that if an error is detected, it is possible to have information about where
the data originated from. Instruction-mix profiling counts the number of ALU,
load, store, and control instructions that are executed. This profiling
information can be useful for performing optimizations. Additionally, recent
work has shown that this information can be used to detect malicious software \cite{tang-raid14}.
LockSet attempts to detect possible race conditions in multi-threaded programs
by associating information about which locks have access to shared memory
locations. If a shared memory location is accessed without the use of a lock
then a race condition may exist.
Note that, although our dataflow engine performs similar operations to the DIFT
monitor, the dataflow engine operates on smaller, 2-bit flags.

@@

Figure~\ref{fig:evaluation.filtering} shows the
normalized execution times with filtering enabled. We see significant
reductions in overhead for all three monitoring schemes. UMC sees normalized
execution times of 1.7-7x with an average of 4x with null metadata filtering.
This is an average reduction in overheads of 65\%. For BC, normalized execution
times drop from 16x down to 3x on average (an 80\% reduction). The range of normalized execution
times for filtered BC is 1.1-8.3x. 
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
Finally, DIFT sees the largest reduction in overheads with only 10\% overheads
on average after filtering, an 88\% reduction in monitoring overheads, with a
maximum overhead of 31\% after filtering. This is due, in part, to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. For most of these
benchmarks, this propagates to relatively few instructions. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would expect to see less filtering. IMP does not have
null metadata and thus is not affected by null metadata filtering.
LS (not shown) had 1.03-1.72x after null metadata filtering and average
overhead observed was 1.33x for the SPLASH-2 benchmarks.
These overheads are similar to previous results for multi-core monitoring with
minimal hardware costs such as LBA \cite{lba-asid06} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.

@@

Although the overheads of DIFT are quite low after filtering, BC and UMC still
show significant overheads. Similarly, the overheads of IMP are not improved by filtering. In this section, we evaluate the effectiveness of
using partial monitoring (in addition to filtering) to trade-off coverage for further reduced overheads.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. 
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. 
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.

We see that by varying the overhead budget, the coverage achieved also varies.
With only a 1.1x overhead target, array bounds check still
achieves 84\% monitoring coverage on average. The high coverage
achieved with such low overheads is due to two main effects.  The first is that
monitoring can be done in parallel, providing monitoring coverage without
introducing overheads. The second effect is that, although we aggressively
filter out monitoring events, there may still exist a large number of
monitoring events that do not lead to security or reliability checks. As a
result, dropping these events can reduce overheads without a large impact on
monitoring coverage.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring. We see that
with a 1.1x overhead target, UMC achieves 25\% monitoring coverage on average.
By increasing this overhead budget to 1.5x, UMC achieves 43\% coverage on
average. Even higher coverage can be achieved by allowing higher overheads.
Similarly, Figure~\ref{fig:evaluation.ls_sweep} shows the coverage achieved by LS.
With a 1.1x overhead, LS achieves 53\% coverage on average. This increases to
71\% coverage with a 1.2x overhead. 
\DAN{Try to explain water\_nsquared results not reaching 100\%?}

@@

In addition to evaluating our system for a core-based monitor, we also
evaluated partial monitoring on a higher performance FPGA-based monitor. This
setup is based on the FlexCore \cite{flexcore-micro10} setup and uses a
fully-pipelined monitor running on an FPGA fabric at half the frequency of the
main core. We show results only for UMC. In this case, full overheads of
monitoring range from 10-70\%. Figure~\ref{fig:evaluation.fpga_umc_sweep} shows
the coverage achieved as we sweep overhead from 1-70\%. We see that partial
monitoring can allow the overheads of such a system to be pushed below 10\%
while still providing partial coverage.

@@

In this section we evaluate the trade-offs between unrestricted dropping and source-only dropping.
The results are shown for an overhead target of 1.5x.
Figure~\ref{fig:evaluation.umc_exec_time} shows the difference between the
overhead budget and the run-time monitoring overheads for UMC. A positive value
means that the overhead target was overshot while a negative value indicates
that the overhead budget was met. We see similar results for unrestricted
dropping and source-only dropping due to the fact that UMC consists of a large
number of independent monitoring flows.
Figure~\ref{fig:evaluation.umc_coverage} shows the coverage of UMC for
unrestricted dropping and source-only dropping. We see that, in several cases, source-only dropping
achieves higher coverage than unrestricted dropping. On average, unrestricted
dropping achieves 46\% coverage while source-only dropping achieves 49\%
coverage. This is due
to the fact that some of the overheads of monitoring for unrestricted dropping
are being spent on wasted work as discussed in Section~\ref{sec:policies.which}.

@@

Next, we evaluate these trade-offs between source-only dropping and unrestricted dropping for BC.
Figure~\ref{fig:evaluation.bc_exec_time} shows the overhead differences for BC
and Figure~\ref{fig:evaluation.bc_coverage} shows the coverage for BC.
From Figure~\ref{fig:evaluation.bc_exec_time}, we see that for several
benchmarks, source-only drop fails to meet the specified overhead target.
The overshoot of the overhead target is quite high with an overhead differences
of 420\% for {\tt bzip2}, 120\% for {\tt gcc}, and 1500\% for {\tt hmmer}.
Since only array allocations are considered source events for BC, it is
difficult for source-only dropping to match overhead targets. Although
Figure~\ref{fig:evaluation.bc_coverage} shows higher coverage for
source-only dropping, this is largely due to the fact that is running with
higher overheads.

@@

One possible application of partial monitoring with low overheads is to enable
cooperative debugging. 
The idea with cooperative debugging is to use partial
monitoring with very low overheads across a large number of users or runs. By
varying the pattern of partial monitoring done on each run, the goal is to
achieve high coverage across multiple runs. Varying the monitoring that is
done for different runs can be achieved by using a probabilistic dropping policy.
Figure~\ref{fig:evaluation.multirun} shows the total
coverage achieved over multiple runs for array bounds check running for
unrestricted and source-only dropping policies with probabilistic dropping.
These numbers are averaged across all benchmarks. Here, we use a 10\%
probability
that events are not dropped. Since the goal is code coverage, coverage here is
measured as the percentage of static instructions which are monitored. Each run
was simulated for 200 million instructions. 
We see that for the unrestricted dropping policy there is almost no increase in
coverage.  This is due to the fact that since there are multiple dependent
monitoring operations that must be done in order for a final check to be
successful as discussed in Section~\ref{sec:policies.when}.
Instead, source-only
dropping is much better suited for achieving high coverage over multiple runs.
Source-only dropping shows a 5\% increase in coverage with only seven runs.
Over hundreds or thousands of runs, source-only dropping should be able to
reach 100\% code coverage.

>>>>

We implemented our dataflow-guided monitoring architecture by
modifying the ARM version of the gem5 simulator \cite{gem5} to support parallel
run-time monitoring. We implement the monitor as a software-based monitor
running on a parallel processor core. We model the main and monitoring cores as
running at 2.5
GHz with 4-way set-associative private L1 I/D caches and a shared 8-way 2 MB L2
cache. This setup is similar to the Snapdragon 801 processor commonly found in
mobile systems. The dataflow engine uses a 1 kB cache for flags.

In order to explore the generality of the architecture for
different monitors, we implemented five different monitors: uninitialized
memory check (UMC), array bounds check (BC), dynamic information flow
tracking (DIFT), instruction-mix profiling (IMP), and LockSet-based race detection (LS).  Uninitialized memory
check seeks to detect loading from
memory locations that are not initialized first. Array bounds check, as
mentioned in Section~\ref{sec:monitoring}, is a monitoring scheme that aims to
detect buffer overflows where memory accesses go beyond the boundaries of an
array. We modify the implementation of {\tt malloc} to set base and bound
metadata information. Dynamic information flow tracking is a security
monitoring scheme
which detects when information from untrusted sources is used to affect the
program control flow (i.e., indirect control instructions). For the benchmarks we consider, we mark data read from
files as untrusted. We implemented a multi-bit DIFT scheme which marks
untrusted data with a 32-bit metadata identifier so
that if an error is detected, it is possible to have information about where
the data originated from. Instruction-mix profiling counts the number of ALU,
load, store, and control instructions that are executed. This profiling
information can be useful for performing optimizations. Additionally, recent
work has shown that this information can be used to detect malicious software \cite{tang-raid14}.
LockSet attempts to detect possible race conditions in multi-threaded programs
by associating information about which locks have access to shared memory
locations. If a shared memory location is accessed without the use of a lock
then a race condition may exist. Since we implement the monitor using a
processor core and our dataflow engine was designed to be generally applicable,
the same hardware platform supports all of these monitoring techniques.

@@

Figure~\ref{fig:evaluation.filtering} shows the
normalized execution times with filtering enabled. We see significant
reductions in overhead for all three monitoring schemes. UMC sees normalized
execution times of 1.7-7x with an average of 4x with null metadata filtering.
For BC, normalized execution
times drop from 16x down to 3x on average. The range of normalized execution
times for filtered BC is 1.1-8.3x. 
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
Finally, DIFT sees the largest reduction in overheads with only 10\% overheads
on average after filtering, with a
maximum overhead of 31\% after filtering. This is due, in part, to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. For most of these
benchmarks, this propagates to relatively few instructions. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would expect to see less filtering. IMP does not have
null metadata and thus is not affected by null metadata filtering.
Overheads for LS (not shown) are 1.03-1.72x after null metadata filtering and the average
overhead observed is 1.33x for the SPLASH-2 benchmarks.
These overheads are similar to previous results for multi-core monitoring with
minimal hardware costs such as LBA \cite{lba-asid06} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.

@@

In this section, we evaluate the effectiveness of
using partial monitoring (in addition to filtering) to trade-off coverage for further reduced overheads.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. 
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. 
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.

We see that by varying the overhead budget, the coverage achieved also varies.
With only a 1.1x overhead target (10\% slowdown), array bounds check still
achieves 84\% monitoring coverage on average. The high coverage
achieved with such low overheads is due to two main effects.  The first is that
monitoring can be done in parallel, providing a certain level of monitoring coverage without
introducing overheads. The second effect is that, although we aggressively
filter out monitoring events, there may still exist a large number of
monitoring events that do not lead to security or reliability checks. As a
result, dropping these events can reduce overheads without a large impact on
monitoring coverage.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring. We see that
with a 1.1x overhead target, UMC achieves 25\% monitoring coverage on average.
By increasing this overhead budget to 1.5x, UMC achieves 43\% coverage on
average. Even higher coverage can be achieved by allowing higher overheads.
Similarly, Figure~\ref{fig:evaluation.ls_sweep} shows the coverage achieved by LS.
With a 1.1x overhead, LS achieves 53\% coverage on average. This increases to
71\% coverage with a 1.2x overhead. 
Since the overheads of DIFT are low to begin with, setting an overhead target
1.1x is enough for all benchmarks tested to reach 100\% coverage.
\DAN{Try to explain water\_nsquared results not reaching 100\%?}

@@

In addition to evaluating our system for a core-based monitor, we also
evaluated partial monitoring on a higher performance FPGA-based monitor. This
setup is based on the FlexCore \cite{flexcore-micro10} setup and uses a
fully-pipelined monitor running on an FPGA fabric at half the frequency of the
main core. We show results for UMC due to space constraints though other
monitors show similar trends. In this case, full overheads of
monitoring range from 1.1-1.7x. Figure~\ref{fig:evaluation.fpga_umc_sweep} shows
the coverage achieved as we sweep overhead from 1.01-1.7x. We see that partial
monitoring can allow the overheads of such a system to be pushed below 10\%
while still providing over 50\% coverage.

@@

In this section we evaluate the trade-offs between unrestricted dropping and source-only dropping.
The results are shown for an overhead target of 1.5x.
Figure~\ref{fig:evaluation.umc_exec_time} shows the difference between the
overhead budget and the run-time monitoring overheads for UMC. A positive value
means that the overhead target was overshot while a negative value indicates
that the overhead budget was met. We see similar results for unrestricted
dropping and source-only dropping due to the fact that UMC consists of a large
number of short, independent monitoring chains.
Figure~\ref{fig:evaluation.umc_coverage} shows the coverage of UMC for
unrestricted dropping and source-only dropping. We see that, in several cases, source-only dropping
achieves higher coverage than unrestricted dropping. On average, unrestricted
dropping achieves 46\% coverage while source-only dropping achieves 49\%
coverage. This is due
to the fact that some of the overheads of monitoring for unrestricted dropping
are being spent on wasted work as discussed in Section~\ref{sec:policies.which}.

@@

Next, we evaluate these trade-offs between source-only dropping and unrestricted dropping for BC.
Figure~\ref{fig:evaluation.bc_exec_time} shows the overhead differences for BC
and Figure~\ref{fig:evaluation.bc_coverage} shows the coverage for BC.
From Figure~\ref{fig:evaluation.bc_exec_time}, we see that for several
benchmarks, source-only drop fails to meet the specified overhead target.
The overshoot of the overhead target is quite high with an overhead differences
of 420\% for {\tt bzip2}, 120\% for {\tt gcc}, and 1500\% for {\tt hmmer}.
Since only array allocations are considered as source events for BC, it is
difficult for source-only dropping to match overhead targets. Although
Figure~\ref{fig:evaluation.bc_coverage} shows higher coverage for
source-only dropping, this is largely due to the fact that is running with
higher overheads.

@@

One possible application of partial monitoring with low overheads is to enable
cooperative debugging. 
The idea with cooperative debugging is to use partial
monitoring with very low overheads across a large number of users or runs. By
varying the pattern of partial monitoring done on each run, the goal is to
achieve high coverage across multiple runs. Varying the monitoring that is
done for different runs can be achieved by using a probabilistic dropping policy.
Figure~\ref{fig:evaluation.multirun} shows the total
coverage achieved over multiple runs for array bounds check running for
unrestricted and source-only dropping policies with probabilistic dropping.
These numbers are averaged across all benchmarks. Here, we use a 10\%
probability
that events are not dropped. Since the goal is code coverage, coverage here is
measured as the percentage of static instructions which are monitored. Each run
was simulated for 200 million instructions. 
We see that for the unrestricted dropping policy there is almost no increase in
coverage.  This is due to the fact that it is likely that at least one
monitoring event in a chain will be dropped with the unrestricted dropping
policy. 
Instead, source-only
dropping is much better suited for achieving high coverage over multiple runs.
Source-only dropping shows a 5\% increase in coverage with only seven runs.
Over hundreds or thousands of runs, source-only dropping should be able to
reach 100\% code coverage.
